Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-22 paper/paper.tex
added Taras to member list, Adriens father, edited operational safety

The team is made of N Rutgers undergraduates
% List, can we do itemize for this? two columns? needs to be smaller
Anthony Garrison, President
Amanda Gaetano, Vice President
Pat Hickey, Treasurer and Electronics Team Leader
Greg Quinn, Mechanical Team Leader
Stephen Indyk, Cogan Noll, John Palmer, Adrien Perkins, Michael Varga, Bradley Lord, David Wescott, and.....

@@

We would like to acknowledge
(Adrien's Father), for his prolific networking and promotion of the team;
Gregg (last name) of BP Hobbies for getting us out of numerous binds;
Dave Devries and Michael Maia, of Invensense, for their technical guidance;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black;
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

@@

When an image has been fully downloaded to the ground targets can be identified and tagged with metadata.  Information about the plane's orientation, gps coordinates, altitude, yaw/pitch/roll, and pan/tilt of the camera are sent down with the image.  Using this information the GPS location of the target can be determined using the intrinsic properties of the camera and some basic trigonometry. target shape, color, alphanumeric, alphanumeric color, and orienttion are all entered manually by the operator.

@@

\subsection{Safety Features}
Our system is designed to gracefully handle any failure while continuing to ensure the safety of those nearby. 
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Channel 5 (?) allows quick switch to safety pilot in case of autopilot malfunction
	\item autopilot return home command if connection is lost (I presume it does something like that?)
	\item kill switch
	\item etc?
\end{itemize}

\subsection{Procedures}
Our team employs a clearly defined flight routine every time the engine is started.  Blah blah blah.  Maybe just include either the flight routine or pre-flight checklist as an appendix?  I feel like this stuff is pretty standard, and there's probably no point in us wasting a lot of space rambling about it.

>>>>

The team is made of 12 Rutgers undergraduates
% List, can we do itemize for this? two columns? needs to be smaller
Anthony Garrison, President
Amanda Gaetano, Vice President
Pat Hickey, Treasurer and Electronics Team Leader
Greg Quinn, Mechanical Team Leader
Stephen Indyk, Cogan Noll, John Palmer, Adrien Perkins, Michael Varga, Bradley Lord, David Wescott, and Taras Wallace.

@@

We would like to acknowledge
Jeff Perkins, for his prolific networking and promotion of the team;
Gregg (last name) of BP Hobbies for getting us out of numerous binds;
Dave Devries and Michael Maia, of Invensense, for their technical guidance;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black;
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

@@

When an image has been fully downloaded to the ground targets can be identified and tagged with metadata.  Information about the plane's orientation, gps coordinates, altitude, yaw/pitch/roll, and pan/tilt of the camera are sent down with the image.  Using this information the GPS location of the target can be determined using the intrinsic properties of the camera and some basic trigonometry. Target shape, color, alphanumeric, alphanumeric color, and orientation are all entered manually by the operator.

@@

\subsection{Safety Features}
Our system is designed to gracefully handle any failure while continuing to ensure the safety of those nearby. 
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Channel 5 (?) allows quick switch to safety pilot in case of autopilot malfunction.
	\item If the plane loses contact with the ground station for more than XX seconds, the autopilot will default to a ``return home mode'' that will direct the plane towards the groundstation in hopes of reestablishing a connection.  If the connection remains dead for XX minutes, the autopilot will direct the plane to [DO SOMETHING?]
	\item Channel 6 (?) functions as a remote kill switch, ensuring the ability to cut power to the engine if an emergent situation precludes direct manual shut off.
	\item etc?
\end{itemize}

\subsection{Procedures}
Our team employs a clearly defined flight routine every time the engine is started.  This routine ensures that everyone in the starting area is fully alert and aware at all times, that no one stands in a position of known danger (i.e. the prop arc), and that all know when the starter makes contact with the spinner.  A set script with clear key words not only ensures the safety of our team, but also is conducive to efficiency, consistency, and repeatability.
